---
title: "TidyTemplate"
date: 2021-02-08
output: html_document
editor_options: 
  chunk_output_type: console
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(tidytuesdayR)
library(janitor)
library(scales)
library(ggtext)
library(stringi)
library(RColorBrewer)

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-02-09")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```



# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

lifetime_earn <- tt$lifetime_earn
student_debt <- tt$student_debt
retirement <- tt$retirement
home_owner <- tt$home_owner
race_wealth <- tt$race_wealth
income_time <- tt$income_time
income_limits <- tt$income_limits
income_aggregate <- tt$income_aggregate
income_distribution <- tt$income_distribution
income_mean <- tt$income_mean

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
income_distribution %>%
  filter(race %in% c("White Alone", "Black Alone"),
         year %in% c(1969, 2019)) %>%
  select(-income_mean_moe, -income_med_moe) %>%
  mutate(bracket_max = as.numeric(gsub(',', '', stri_extract_last_regex(income_bracket, '\\d+,\\d+')))) %>% 
  mutate(race = factor(race,levels = c("Black Alone", "Hispanic (Any Race)", "White Alone")),
         income_bracket = fct_reorder(income_bracket, -bracket_max),
         year = factor(year)) %>%
  ggplot() +
  geom_bar(aes(x = year, y = income_distribution/100, fill = income_bracket), 
           stat = 'identity', color = 'gray40') +
  scale_fill_brewer(palette = 'PuBu') +
  scale_y_continuous(labels = percent,
                     sec.axis = dup_axis()) +
  labs(x = NULL,
       y = NULL,
       fill = 'Income Bracket',
       title = 'Income distribution after 50 years',
       subtitle = glue::glue('40.1% of black households in 2019 make under 35K. 
                             That\'s a higher percentage than white households in 1969.')) +
  theme(panel.grid = element_blank(), 
        plot.background = element_rect(fill = 'grey'),
        panel.background = element_rect(fill = 'grey',
                                        linetype = 'blank'),
        legend.background = element_rect(fill = 'grey'),
        strip.background = element_rect(fill = 'grey'),
        strip.text = element_text(family = 'serif', size = 14),
        axis.text = element_text(color = 'black')) +
  facet_wrap(~race)

race_wealth %>%
  filter(type == 'Median') %>%
  ggplot(aes(year, wealth_family, color = race)) +
  geom_line() +
  facet_wrap(~type)

colors <- c('black_pct' = '#2B8CBE', 'hisp_pct' = '#E6550D')
income_mean %>% 
  filter(dollar_type == '2019 Dollars',
         race %in% c("White Alone", "Black Alone", "Hispanic")) %>%
  pivot_wider(names_from = race, values_from = income_dollars) %>%
  mutate(hisp_pct = `Hispanic` / `White Alone`,
         black_pct = `Black Alone`   / `White Alone`) %>%
  #pivot_longer(c(`Hispanic`, `Black Alone`, `White Alone`), 
               #names_to = 'race', values_to = 'income_dollars') %>%
  pivot_longer(c(hisp_pct, black_pct), names_to = 'relation', values_to = 'percentage') %>%
  mutate(income_quintile = factor(income_quintile, 
                                  levels = c("Lowest", "Second", "Middle", 
                                             "Fourth", "Highest", "Top 5%"))) %>%
  filter(!is.na(percentage)) %>%
  ggplot(aes(year, percentage, color = relation)) +
  geom_line(show.legend = FALSE) +
  facet_wrap(~income_quintile) +
  scale_y_continuous(labels = percent, 
                     limits = c(0, 1)) +
  scale_color_manual(values = colors) +
  labs(x = NULL,
       y = NULL,
       title = 'Average income relative to White households',
        subtitle = glue::glue("Both <span style = 'color:{colors['black_pct']}\'>Black</span> and 
        <span style = 'color:{colors['hisp_pct']}'>Hispanic</span> 
        households earn less, regardless of their income level."),
       color = 'Households') +
  theme_minimal() +
  theme(plot.subtitle = element_markdown())


```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "2021_Week_07/2021_Week_07.png",
  device = "png")

```
